---
title: "1st _ Draft"
output: html_document
date: "2025-11-21"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


Preamble
```{r}
library(tidyverse)
household<- read_csv("~/GitHub/AFRE_Project_Rahman/Raw_Data/faps_household_puf.csv")
Individual<- read_csv("~/GitHub/AFRE_Project_Rahman/Raw_Data/faps_individual_puf.csv")
fahNutrient <- read_csv("~/GitHub/AFRE_Project_Rahman/Raw_Data/faps_fahnutrients.csv")
FafHNutrient <- read_csv("~/GitHub/AFRE_Project_Rahman/Raw_Data/faps_fafhnutrient_puf.csv")
```

#Table 1 
## Table 1. Summary Statistics
### To construct the mean values that are seen in the Courmacnhe et al paper i ahve attached the table with all the variables listed out 

| Variable | Mean | Std. Error |
|---------|------|------------|
| **SNAP participation** |  |  |
| Self-reported (REPORT) |  |  |
| Administrative caseload (ADMIN) |  |  |
| Administrative EBT (ALERT) |  |  |
| **Dependent variables** |  |  |
| Low food security |  |  |
| Very low food security |  |  |
| Total 2010 HEI score |  |  |
| Body mass index |  |  |
| Obese |  |  |
| Severely obese |  |  |
| **Control variables** |  |  |
| Age (years) |  |  |
| Female |  |  |
| Black |  |  |
| White |  |  |
| Other race |  |  |
| Married |  |  |
| Formerly married |  |  |
| Household size |  |  |
| Number of children |  |  |
| Rural tract |  |  |
| Less than high school |  |  |
| High school graduate |  |  |
| Some college |  |  |
| College degree or higher |  |  |
| Worked last week |  |  |
| Gross monthly income (\$1000s) |  |  |
| Child < 5 in HH |  |  |
| Elderly ≥ 65 in HH |  |  |
| Never married |  |  |
| Miles to primary food store |  |  |
| Primary store SNAP-authorized |  |  |

**Notes:** Statistics are from the main analysis sample of 2,108 observations. Weighted using FoodAPS complex design.


```{r}
colnames(household)
```

```{r}
# Extracting the Columns to construct Table one
household_1 <- household %>%
  select(
    # Primary Key
    hhnum,
    # SNAP participation
    snapnowreport,
    snapnowadmin,
    snapnowhh,
    matchconsenthh,
    # Dependent variables
    adltfsraw, # May need to remove
    adltfscat,
    # Controls
    hhsize,
    rural,
    inchhavg_r,
    primstoredist_d,
    primstoresnaptype,
  )

```

```{r}
Individual_1 <- Individual %>%
  select(
    #Primary Key
    HHNUM,
    #DEPENDENT vARIABKE
    BMI,
    #cONTROLS
    SEX,
    RACECAT_R,
    MARITAL,
    EMPLOYMENT,
    EDUCCAT,
    AGE_R,
    EMPLOYMENT)
```


# Construct The HEI


