---
title: "1st _ Draft"
output: html_document
date: "2025-11-21"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


Preamble
```{r}
library(tidyverse)
household<- read_csv("~/GitHub/AFRE_Project_Rahman/Raw_Data/faps_household_puf.csv")
Individual<- read_csv("~/GitHub/AFRE_Project_Rahman/Raw_Data/faps_individual_puf.csv")
fahNutrient <- read_csv("~/GitHub/AFRE_Project_Rahman/Raw_Data/faps_fahnutrients.csv")
fafHNutrient <- read_csv("~/GitHub/AFRE_Project_Rahman/Raw_Data/faps_fafhnutrient_puf.csv")
faps_fahitem <- read_csv("~/GitHub/AFRE_Project_Rahman/Raw_Data/faps_fahitem_puf.csv")
faps_fafhitem <- read_csv("~/GitHub/AFRE_Project_Rahman/Raw_Data/faps_fafhitem_puf.csv")
```

#Table 1 
## Table 1. Summary Statistics
### To construct the mean values that are seen in the Courmacnhe et al paper i ahve attached the table with all the variables listed out 

| Variable | Mean | Std. Error |
|---------|------|------------|
| **SNAP participation** |  |  |
| Self-reported (REPORT) |  |  |
| Administrative caseload (ADMIN) |  |  |
| Administrative EBT (ALERT) |  |  |
| **Dependent variables** |  |  |
| Low food security |  |  |
| Very low food security |  |  |
| Total 2010 HEI score |  |  |
| Body mass index |  |  |
| Obese |  |  |
| Severely obese |  |  |
| **Control variables** |  |  |
| Age (years) |  |  |
| Female |  |  |
| Black |  |  |
| White |  |  |
| Other race |  |  |
| Married |  |  |
| Formerly married |  |  |
| Household size |  |  |
| Number of children |  |  |
| Rural tract |  |  |
| Less than high school |  |  |
| High school graduate |  |  |
| Some college |  |  |
| College degree or higher |  |  |
| Worked last week |  |  |
| Gross monthly income (\$1000s) |  |  |
| Child < 5 in HH |  |  |
| Elderly ≥ 65 in HH |  |  |
| Never married |  |  |
| Miles to primary food store |  |  |
| Primary store SNAP-authorized |  |  |

**Notes:** Statistics are from the main analysis sample of 2,108 observations. Weighted using FoodAPS complex design.


```{r}
colnames(household)
```

```{r}
# Extracting the Columns to construct Table one
household_1 <- household %>%
  select(
    # Primary Key
    hhnum,
    # SNAP participation
    snapnowreport,
    snapnowadmin,
    snapnowhh,
    matchconsenthh,
    # Dependent variables
    adltfsraw, # May need to remove
    adltfscat,
    # Controls
    hhsize,
    rural,
    inchhavg_r,
    primstoredist_d,
    primstoresnaptype,
  )

```

```{r}
Individual_1 <- Individual %>%
  select(
    #Primary Key
    HHNUM,
    #DEPENDENT vARIABKE
    BMI,
    #cONTROLS
    SEX,
    RACECAT_R,
    MARITAL,
    EMPLOYMENT,
    EDUCCAT,
    AGE_R,
    EMPLOYMENT)
```


```{r}
Individual_1 <- Individual_1 %>%
  rename(hhnum = HHNUM)
```


```{r}
Table_1_data_frame <- household_1 %>%
  left_join(Individual_1, by = "hhnum")
```

```{r}
Table_1_data_frame <- Table_1_data_frame %>% 
  mutate(
    Obese = ifelse(BMI >= 30, 1, 0),
    Severely_Obese = ifelse(BMI >= 35, 1, 0),
    # Create a self-reported SNAP variable:
    # Keep values 0 (No) and 1 (Yes); set all other codes (e.g., -997, -998) to NA
    SNAP_REPORT = ifelse(snapnowreport %in% c(0,1), snapnowreport, NA),
    # Create an administrative SNAP variable:
    # Keep values 0 (No) and 1 (Yes); set all other codes (e.g., 2, -996) to NA
    SNAP_ADMIN = ifelse(snapnowadmin %in% c(0,1), snapnowadmin, NA),
    # Create a combined household SNAP variable:
    # Keep values 0 (No) and 1 (Yes); set all other codes to NA
    SNAP_HH = ifelse(snapnowhh %in% c(0,1), snapnowhh, NA),
    foodsec_lowvlow = factor(
      adltfscat %in% c(3, 4),
      levels = c(FALSE, TRUE),
      labels = c("Low food security", "Very low food security")
    )
  )

    
  )
```

```{r}
colnames(Table_1_data_frame)
```

```{r}
colnames(Table_1_data_frame$snapnowreport)

```



# Construct The HEI

The Healthy Eating Index is a widely used measure of overall dietary quality, designed to align with the 2010 Dietary Guidelines for Americans. Because FoodAPS provides individual food-level nutrient data for foods acquired at home (FAH) and away from home (FAFH), the HEI must be reconstructed manually through a multi-step process. Below, I describe each stage of the workflow and the reasoning behind it.


### Merge FAH and FAFH nutrient files with item-level gram weights


```{r}
fah_item_hei <- faps_fahitem
Fafh_item_hei <- faps_fafhitem
fah_nutrient_hei <- fahNutrient
fafh_nutrient_hei <- fafHNutrient

```

####Fah
```{r}
fah_item_hei <- fah_item_hei %>%
  mutate(
    grams_edible = coalesce(
      "totgramsedible",
      "totgramsedibleimp",
      "totgramsunadj",
      "totgramsunadjimp"
    )
  )

```

```{r}
fah_nutrient_hei <- fah_nutrient_hei %>%
  mutate(
    grams_edible = coalesce(
      "totgramsedible",
      "totgramsedibleimp",
      "totgramsunadj",
      "totgramsunadjimp"
    )
  )

```


```{r}
fah_full_hei <- fah_nutrient_hei %>%
  left_join(fah_item_hei, by = c("hhnum","eventid","itemnum"))
```


####Fafh
```{r}
Fafh_item_hei <- Fafh_item_hei %>%
  mutate(
    grams_edible = coalesce(
      "totgramsedible",
      "totgramsedibleimp",
      "totgramsunadj",
      "totgramsunadjimp"
    )
  )

```

```{r}
fafh_nutrient_hei <- fafh_nutrient_hei %>%
  mutate(
    grams_edible = coalesce(
      "totgramsedible",
      "totgramsedibleimp",
      "totgramsunadj",
      "totgramsunadjimp"
    )
  )

```

```{r}
fafh_full_hei <- fafh_nutrient_hei %>%
  left_join(Fafh_item_hei, by = c("hhnum","eventid","itemnum"))
```



#####Combine
```{r}
HEI_ALL <- bind_rows(
  fah_full_hei %>% mutate(source = "FAH"),
  fafh_full_hei %>% mutate(source = "FAFH")
)
```

HEI_next

```{r}
HEI_ALL <- HEI_ALL %>%
  group_by(hhnum) %>%
  summarise(
    energy     = sum(energy, na.rm = TRUE),

    # Dairy
    d_total    = sum(d_total, na.rm = TRUE),

    # Fruits
    f_total    = sum(f_total, na.rm = TRUE),
    f_whole    = sum(f_other, na.rm = TRUE),
    f_juice    = sum(f_juice, na.rm = TRUE),

    # Vegetables
    v_total    = sum(v_total, na.rm = TRUE),
    v_dark     = sum(v_drkgr, na.rm = TRUE),
    v_legumes  = sum(v_legumes, na.rm = TRUE),

    # Grains
    g_whole    = sum(g_whole, na.rm = TRUE),
    g_refined  = sum(g_refined, na.rm = TRUE),

    # Proteins
    pf_total   = sum(pf_total, na.rm = TRUE),
    pf_plant   = sum(pf_soy + pf_nutsds + pf_legumes, na.rm = TRUE),
    pf_seafood = sum(pf_seafd_hi + pf_seafd_low, na.rm = TRUE),

    # Fatty acids
    satfat     = sum(satfat, na.rm = TRUE),
    monofat    = sum(monofat, na.rm = TRUE),
    polyfat    = sum(polyfat, na.rm = TRUE),

    # Sodium / empty calories
    sodium     = sum(sodium, na.rm = TRUE),
    solid_fats = sum(solid_fats, na.rm = TRUE),
    add_sugars = sum(add_sugars, na.rm = TRUE)
  )

```


```{r}
hei_components <- HEI_ALL %>%
  mutate(
    kcal1000 = energy / 1000,

    # HEI-2010 per 1000 kcal components
    fruit_total     = f_total / kcal1000,
    fruit_whole     = f_whole / kcal1000,
    veg_total       = v_total / kcal1000,
    greens_beans    = (v_dark + v_legumes) / kcal1000,

    whole_grains    = g_whole / kcal1000,
    dairy_comp      = d_total / kcal1000,

    protein_total   = pf_total / kcal1000,
    seaplant        = (pf_plant + pf_seafood) / kcal1000,

    fatty_acid_ratio = (monofat + polyfat) / satfat,

    # Moderation (lower = better)
    sodium_kcal      = sodium / kcal1000,
    refined_grains   = g_refined / kcal1000,

    # Empty calories (percentage of total kcal)
    pct_empty = 100 * (
      solid_fats*9 + add_sugars*4
    ) / energy
  )

```

```{r}
hei_scores <- hei_components %>%
  mutate(

    # Adequacy (higher is better)
    score_totfruit     = pmin(5,  fruit_total     / 0.8),
    score_wholefruit   = pmin(5,  fruit_whole     / 0.4),
    score_totalveg     = pmin(5,  veg_total       / 1.1),
    score_greensbeans  = pmin(5,  greens_beans    / 0.2),

    score_wholegrains  = pmin(10, whole_grains    / 1.5),
    score_dairy        = pmin(10, dairy_comp      / 1.3),

    score_protein      = pmin(5,  protein_total   / 2.5),
    score_seaplant     = pmin(5,  seaplant        / 0.8),

    # Fatty acid ratio
    score_fattyacid    = pmin(10, fatty_acid_ratio / 2.5),

    # Moderation (reverse scoring)
    score_sodium  = pmax(0, 10 * ( (2.0 - sodium_kcal) / (2.0 - 1.1) )),
    score_refined = pmax(0, 10 * ( (4.3 - refined_grains) / (4.3 - 1.8) )),

    # Empty calories % of total
    score_empty   = pmax(0, 20 * ( (50 - pct_empty) / (50 - 19) )),

    # Total HEI score (0 to 100)
    hei_total = rowSums(across(starts_with("score_")))
  )

```

