---
title: "1st _ Draft"
output: html_document
date: "2025-11-21"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


Preamble
```{r}
library(tidyverse)
household<- read_csv("~/GitHub/AFRE_Project_Rahman/Raw_Data/faps_household_puf.csv")
Individual<- read_csv("~/GitHub/AFRE_Project_Rahman/Raw_Data/faps_individual_puf.csv")
fahNutrient <- read_csv("~/GitHub/AFRE_Project_Rahman/Raw_Data/faps_fahnutrients.csv")
fafHNutrient <- read_csv("~/GitHub/AFRE_Project_Rahman/Raw_Data/faps_fafhnutrient_puf.csv")
faps_fahitem <- read_csv("~/GitHub/AFRE_Project_Rahman/Raw_Data/faps_fahitem_puf.csv")
faps_fafhitem <- read_csv("~/GitHub/AFRE_Project_Rahman/Raw_Data/faps_fafhitem_puf.csv")
```

#Table 1 
## Table 1. Summary Statistics
### To construct the mean values that are seen in the Courmacnhe et al paper i ahve attached the table with all the variables listed out 

| Variable | Mean | Std. Error |
|---------|------|------------|
| **SNAP participation** |  |  |
| Self-reported (REPORT) |  |  |
| Administrative caseload (ADMIN) |  |  |
| Administrative EBT (ALERT) |  |  |
| **Dependent variables** |  |  |
| Low food security |  |  |
| Very low food security |  |  |
| Total 2010 HEI score |  |  |
| Body mass index |  |  |
| Obese |  |  |
| Severely obese |  |  |
| **Control variables** |  |  |
| Age (years) |  |  |
| Female |  |  |
| Black |  |  |
| White |  |  |
| Other race |  |  |
| Married |  |  |
| Formerly married |  |  |
| Household size |  |  |
| Number of children |  |  |
| Rural tract |  |  |
| Less than high school |  |  |
| High school graduate |  |  |
| Some college |  |  |
| College degree or higher |  |  |
| Worked last week |  |  |
| Gross monthly income (\$1000s) |  |  |
| Child < 5 in HH |  |  |
| Elderly ≥ 65 in HH |  |  |
| Never married |  |  |
| Miles to primary food store |  |  |
| Primary store SNAP-authorized |  |  |

**Notes:** Statistics are from the main analysis sample of 2,108 observations. Weighted using FoodAPS complex design.


```{r}
colnames(household)
```


```{r}
library(tidyverse)

# Prepare household-level variables
household_1 <- household %>%
  select(
    hhnum,
    snapnowreport,
    snapnowadmin,
    snapnowhh,
    matchconsenthh,
    adltfsraw,
    adltfscat,
    pctpovguidehh_r,
    hhwgt,
    tspsu,
    tsstrata,
    hhsize,
    rural,
    inchhavg_r,
    primstoredist_d,
    primstoresnaptype
  )

# Prepare individual-level variables
Individual_1 <- Individual %>%
  select(
    HHNUM,
    BMI,
    SEX,
    RACECAT_R,
    MARITAL,
    EMPLOYMENT,
    EDUCCAT,
    AGE_R
  ) %>%
  rename(hhnum = HHNUM)

# Aggregate household-level age variables
children_elderly <- Individual_1 %>%
  group_by(hhnum) %>%
  summarise(
    Number_of_children = sum(AGE_R < 18, na.rm = TRUE),
    child_lt5 = as.numeric(sum(AGE_R < 5, na.rm = TRUE) > 0),
    elderly_65 = as.numeric(sum(AGE_R >= 65, na.rm = TRUE) > 0),
    .groups = "drop"
  )

# Merge household + individual + aggregated household-level age variables
Table_1_data_frame <- household_1 %>%
  left_join(Individual_1, by = "hhnum") %>%
  left_join(children_elderly, by = "hhnum") %>%
  mutate(
    # BMI / Obesity
    Obese = ifelse(BMI >= 30, 1, 0),
    Severely_Obese = ifelse(BMI >= 35, 1, 0),
    
    # SNAP
    SNAP_REPORT = ifelse(snapnowreport %in% c(0,1), snapnowreport, NA),
    SNAP_ADMIN = ifelse(snapnowadmin %in% c(0,1), snapnowadmin, NA),
    SNAP_HH = ifelse(snapnowhh %in% c(0,1), snapnowhh, NA),
    
    # Food security
    foodsec_low = case_when(
      adltfscat == 3 ~ 1,  # Low food security
      TRUE ~ 0
    ),
    foodsec_verylow = case_when(
      adltfscat == 4 ~ 1,  # Very low food security
      TRUE ~ 0
    ),
    
    # Sex
    Female = case_when(
      SEX == 2 ~ 1,
      SEX == 1 ~ 0,
      TRUE ~ NA_real_
    ),
    
    # Race indicators
    race_white = ifelse(RACECAT_R == 1, 1, 0),
    race_black = ifelse(RACECAT_R == 2, 1, 0),
    race_other = ifelse(RACECAT_R %in% c(3,4,5,6), 1, 0),
    
    # Marital status
    marital_married = ifelse(MARITAL == 1, 1, 0),
    marital_formerly = ifelse(MARITAL %in% c(2,3,4), 1, 0),
    marital_never = ifelse(MARITAL == 5, 1, 0),
    
    # Education
    edu_less_hs = ifelse(EDUCCAT %in% c(1,2), 1, 0),
    edu_hs = ifelse(EDUCCAT == 3, 1, 0),
    edu_some_college = ifelse(EDUCCAT == 4, 1, 0),
    edu_college_plus = ifelse(EDUCCAT %in% c(5,6), 1, 0),
    
    # SNAP-authorized store indicator
    primstore_snapauth = case_when(
      primstoresnaptype == "BC" ~ 0,              # Not SNAP authorized
      is.na(primstoresnaptype) ~ NA_real_,        # Missing
      TRUE ~ 1), 
    
    # Employment
    worked_last_week = case_when(
      EMPLOYMENT %in% c(1,2,3) ~ 1,
      EMPLOYMENT %in% c(4,5) ~ 0,
      EMPLOYMENT %in% c(-996,-998,-997) ~ NA_real_
    ))

```




# Construct The HEI

The Healthy Eating Index is a widely used measure of overall dietary quality, designed to align with the 2010 Dietary Guidelines for Americans. Because FoodAPS provides individual food-level nutrient data for foods acquired at home (FAH) and away from home (FAFH), the HEI must be reconstructed manually through a multi-step process. Below, I describe each stage of the workflow and the reasoning behind it.


### Merge FAH and FAFH nutrient files with item-level gram weights


```{r}
fah_item_hei <- faps_fahitem
Fafh_item_hei <- faps_fafhitem
fah_nutrient_hei <- fahNutrient
fafh_nutrient_hei <- fafHNutrient

```

####Fah
```{r}
fah_item_hei <- fah_item_hei %>%
  mutate(
    grams_edible = coalesce(
      "totgramsedible",
      "totgramsedibleimp",
      "totgramsunadj",
      "totgramsunadjimp"
    )
  )

```

```{r}
fah_nutrient_hei <- fah_nutrient_hei %>%
  mutate(
    grams_edible = coalesce(
      "totgramsedible",
      "totgramsedibleimp",
      "totgramsunadj",
      "totgramsunadjimp"
    )
  )

```


```{r}
fah_full_hei <- fah_nutrient_hei %>%
  left_join(fah_item_hei, by = c("hhnum","eventid","itemnum"))
```


####Fafh
```{r}
Fafh_item_hei <- Fafh_item_hei %>%
  mutate(
    grams_edible = coalesce(
      "totgramsedible",
      "totgramsedibleimp",
      "totgramsunadj",
      "totgramsunadjimp"
    )
  )

```

```{r}
fafh_nutrient_hei <- fafh_nutrient_hei %>%
  mutate(
    grams_edible = coalesce(
      "totgramsedible",
      "totgramsedibleimp",
      "totgramsunadj",
      "totgramsunadjimp"
    )
  )

```

```{r}
fafh_full_hei <- fafh_nutrient_hei %>%
  left_join(Fafh_item_hei, by = c("hhnum","eventid","itemnum"))
```



#####Combine
```{r}
HEI_ALL <- bind_rows(
  fah_full_hei %>% mutate(source = "FAH"),
  fafh_full_hei %>% mutate(source = "FAFH")
)
```

HEI_next

```{r}
HEI_ALL <- HEI_ALL %>%
  group_by(hhnum) %>%
  summarise(
    energy     = sum(energy, na.rm = TRUE),

    # Dairy
    d_total    = sum(d_total, na.rm = TRUE),

    # Fruits
    f_total    = sum(f_total, na.rm = TRUE),
    f_whole    = sum(f_other, na.rm = TRUE),
    f_juice    = sum(f_juice, na.rm = TRUE),

    # Vegetables
    v_total    = sum(v_total, na.rm = TRUE),
    v_dark     = sum(v_drkgr, na.rm = TRUE),
    v_legumes  = sum(v_legumes, na.rm = TRUE),

    # Grains
    g_whole    = sum(g_whole, na.rm = TRUE),
    g_refined  = sum(g_refined, na.rm = TRUE),

    # Proteins
    pf_total   = sum(pf_total, na.rm = TRUE),
    pf_plant   = sum(pf_soy + pf_nutsds + pf_legumes, na.rm = TRUE),
    pf_seafood = sum(pf_seafd_hi + pf_seafd_low, na.rm = TRUE),

    # Fatty acids
    satfat     = sum(satfat, na.rm = TRUE),
    monofat    = sum(monofat, na.rm = TRUE),
    polyfat    = sum(polyfat, na.rm = TRUE),

    # Sodium / empty calories
    sodium     = sum(sodium, na.rm = TRUE),
    solid_fats = sum(solid_fats, na.rm = TRUE),
    add_sugars = sum(add_sugars, na.rm = TRUE)
  )

```


```{r}
hei_components <- HEI_ALL %>%
  mutate(
    kcal1000 = energy / 1000,

    # HEI-2010 per 1000 kcal components
    fruit_total     = f_total / kcal1000,
    fruit_whole     = f_whole / kcal1000,
    veg_total       = v_total / kcal1000,
    greens_beans    = (v_dark + v_legumes) / kcal1000,

    whole_grains    = g_whole / kcal1000,
    dairy_comp      = d_total / kcal1000,

    protein_total   = pf_total / kcal1000,
    seaplant        = (pf_plant + pf_seafood) / kcal1000,

    fatty_acid_ratio = (monofat + polyfat) / satfat,

    # Moderation (lower = better)
    sodium_kcal      = sodium / kcal1000,
    refined_grains   = g_refined / kcal1000,

    # Empty calories (percentage of total kcal)
    pct_empty = 100 * (
      solid_fats*9 + add_sugars*4
    ) / energy
  )

```

```{r}
hei_scores <- hei_components %>%
  mutate(

    # Adequacy (higher is better)
    score_totfruit     = pmin(5,  fruit_total     / 0.8),
    score_wholefruit   = pmin(5,  fruit_whole     / 0.4),
    score_totalveg     = pmin(5,  veg_total       / 1.1),
    score_greensbeans  = pmin(5,  greens_beans    / 0.2),

    score_wholegrains  = pmin(10, whole_grains    / 1.5),
    score_dairy        = pmin(10, dairy_comp      / 1.3),

    score_protein      = pmin(5,  protein_total   / 2.5),
    score_seaplant     = pmin(5,  seaplant        / 0.8),

    # Fatty acid ratio
    score_fattyacid    = pmin(10, fatty_acid_ratio / 2.5),

    # Moderation (reverse scoring)
    score_sodium  = pmax(0, 10 * ( (2.0 - sodium_kcal) / (2.0 - 1.1) )),
    score_refined = pmax(0, 10 * ( (4.3 - refined_grains) / (4.3 - 1.8) )),

    # Empty calories % of total
    score_empty   = pmax(0, 20 * ( (50 - pct_empty) / (50 - 19) )),

    # Total HEI score (0 to 100)
    hei_total = rowSums(across(starts_with("score_")))
  )

```

```{r}
HEI_Total <- hei_scores %>%
  select(hhnum, hei_total)

# Merge HEI into your main table
Table_1_data_frame <- Table_1_data_frame %>%
  left_join(HEI_Total, by = "hhnum")
```


Making Table 1
```{r}

(Table_1_data_frame$pctpovguidehh_r)
```

```{r}
Table1_sample <- Table_1_data_frame %>%
   mutate(
    across(
    everything(), 
    ~ as.numeric(.))) %>%
  select(-primstoresnaptype) %>%
  filter(matchconsenthh == 1) %>%
  filter(pctpovguidehh_r <= 250)%>%
  filter(if_all(
    .cols = c(
      1:46 # store SNAP authorized
    ),
    ~!is.na(.)
  )) %>%
  distinct(hhnum, .keep_all = TRUE)
```

```{r}



library(survey)

design_t1 <- svydesign(
  ids    = ~tspsu,
  strata = ~tsstrata,
  weights= ~hhwgt,
  nest   = TRUE,
  data   = Table1_sample
)
```



```{r}
svy_mean_foodsec_low <- svymean(~foodsec_low, design_t1, na.rm = TRUE)
```


```{r}
svy_mean_fmt <- function(var, design_t1, label) {
  res <- svymean(as.formula(paste("~", var)), design_t1, na.rm = TRUE)
  mean_val <- as.numeric(res)
  se_val <- as.numeric(SE(res))
  data.frame(
    Variable = label,
    Mean_SE = paste0(round(mean_val, 2), " (", round(se_val, 2), ")"),
    stringsAsFactors = FALSE
  )
}
```


```{r}
table1_list <- list(
  # SNAP participation
  svy_mean_fmt("SNAP_REPORT", design_t1, "Self-reported (REPORT)"),
  svy_mean_fmt("SNAP_ADMIN", design_t1, "Administrative from caseload data (ADMIN)"),
  svy_mean_fmt("SNAP_HH", design_t1, "Administrative from EBT transactions (ALERT)"),
  
  # Dependent variables
  svy_mean_fmt("foodsec_low", design_t1, "Low food security"),
  svy_mean_fmt("foodsec_verylow", design_t1, "Very low food security"),
  svy_mean_fmt("hei_total", design_t1, "Total 2010 HEI score"),
  svy_mean_fmt("BMI", design_t1, "Body mass index"),
  svy_mean_fmt("Obese", design_t1, "Obese"),
  svy_mean_fmt("Severely_Obese", design_t1, "Severely obese"),
  
  # Control variables
  svy_mean_fmt("AGE_R", design_t1, "Age (years)"),
  svy_mean_fmt("Female", design_t1, "Female"),
  svy_mean_fmt("race_black", design_t1, "Black"),
  svy_mean_fmt("race_white", design_t1, "White"),
  svy_mean_fmt("race_other", design_t1, "Other race (non-black, non-white)"),
  svy_mean_fmt("marital_married", design_t1, "Married"),
  svy_mean_fmt("marital_formerly", design_t1, "Formerly married"),
  svy_mean_fmt("hhsize", design_t1, "Household size"),
  svy_mean_fmt("Number_of_children", design_t1, "Number of children"),
  svy_mean_fmt("rural", design_t1, "Rural tract"),
  svy_mean_fmt("edu_less_hs", design_t1, "Less than high school education"),
  svy_mean_fmt("edu_hs", design_t1, "High school graduate"),
  svy_mean_fmt("edu_some_college", design_t1, "Some college education"),
  svy_mean_fmt("edu_college_plus", design_t1, "College degree or higher"),
  svy_mean_fmt("worked_last_week", design_t1, "Worked last week"),
  svy_mean_fmt("pctpovguidehh_r", design_t1, "Gross monthly family income ($1000s)"),
  svy_mean_fmt("child_lt5", design_t1, "Child less than five years present in HH"),
  svy_mean_fmt("elderly_65", design_t1, "Elderly at least 65 years present in HH"),
  svy_mean_fmt("marital_never", design_t1, "Never married"),
  svy_mean_fmt("primstoredist_d", design_t1, "Miles from residence to primary food store"),
  svy_mean_fmt("primstore_snapauth", design_t1, "Primary food store is SNAP-authorized")
)

```

```{r}
Table1_summary <- bind_rows(table1_list)

```

```{r}
Table1_summary

```



```{r}

snap_vars <- c("Self-reported (REPORT)",
               "Administrative from caseload data (ADMIN)",
               "Administrative from EBT transactions (ALERT)")

dep_vars <- c("Low food security",
              "Very low food security",
              "Total 2010 HEI score",
              "Body mass index",
              "Obese",
              "Severely obese")

control_vars <- c("Age (years)",
                  "Female",
                  "Black",
                  "White",
                  "Other race (non-black, non-white)",
                  "Married",
                  "Formerly married",
                  "Household size",
                  "Number of children",
                  "Rural tract",
                  "Less than high school education",
                  "High school graduate",
                  "Some college education",
                  "College degree or higher",
                  "Worked last week",
                  "Gross monthly family income ($1000s)",
                  "Child less than five years present in HH",
                  "Elderly at least 65 years present in HH",
                  "Never married",
                  "Miles from residence to primary food store",
                  "Primary food store is SNAP-authorized")

snap_summary <- Table1_summary %>% filter(Variable %in% snap_vars)
dep_summary <- Table1_summary %>% filter(Variable %in% dep_vars)
control_summary <- Table1_summary %>% filter(Variable %in% control_vars)

header_snap <- data.frame(Variable = "SNAP participation", Mean_SE = "", stringsAsFactors = FALSE)
header_dep <- data.frame(Variable = "Dependent variables", Mean_SE = "", stringsAsFactors = FALSE)
header_control <- data.frame(Variable = "Control variables", Mean_SE = "", stringsAsFactors = FALSE)

Table1_final <- bind_rows(
  header_snap, snap_summary,
  header_dep, dep_summary,
  header_control, control_summary
)

Table1_final


```


```{r}

library(kableExtra)

Table1_final_indented <- Table1_final %>%
  mutate(
    Variable = ifelse(
      Mean_SE != "",                    
      paste0("&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;", Variable),  
      Variable                          
    )
  )

# Render table
Table1_final_indented %>%
  kable(format = "html", escape = FALSE, col.names = c("Variable", "Mean (SE)")) %>%
  kable_styling(
    full_width = TRUE,
    bootstrap_options = c("striped", "hover")
  ) %>%
  add_header_above(c("Table 1. Summary Statistics" = 2), align = "left") %>%
  footnote(
    general = "Notes: Statistics are from main sample. Means and standard errors are survey-weighted."
  )

```




# Table 2 
```{r}
# Prepare household-level variables
household_2 <- household %>%
  select(
    hhnum,
    snapnowreport,
    snapnowadmin,
    snapnowhh,
    matchconsenthh,
    adltfsraw,
    adltfscat,
    pctpovguidehh_r,
    hhwgt,
    tspsu,
    tsstrata,
    hhsize,
    rural,
    inchhavg_r,
    primstoredist_d,
    primstoresnaptype
  )

# Prepare individual-level variables
Individual_2 <- Individual %>%
  select(
    HHNUM,
    BMI,
    SEX,
    RACECAT_R,
    MARITAL,
    EMPLOYMENT,
    EDUCCAT,
    AGE_R
  ) %>%
  rename(hhnum = HHNUM)

# Aggregate household-level age variables
children_elderly <- Individual_2 %>%
  group_by(hhnum) %>%
  summarise(
    Number_of_children = sum(AGE_R < 18, na.rm = TRUE),
    child_lt5 = as.numeric(sum(AGE_R < 5, na.rm = TRUE) > 0),
    elderly_65 = as.numeric(sum(AGE_R >= 65, na.rm = TRUE) > 0),
    .groups = "drop"
  )



# Merge household + individual + aggregated household-level age variables
Table_2_data_frame <- household_2 %>%
  left_join(Individual_2, by = "hhnum") %>%
  left_join(children_elderly, by = "hhnum") %>%
  mutate(
    # BMI / Obesity
    Obese = ifelse(BMI >= 30, 1, 0),
    Severely_Obese = ifelse(BMI >= 35, 1, 0),
      # Set NA for “don’t know/refused” codes
    snapnowhh = ifelse(snapnowhh %in% c(-997), NA, snapnowhh),
    snapnowreport = ifelse(snapnowreport %in% c(-997, -998), NA, snapnowreport),
    snapnowadmin = ifelse(snapnowadmin %in% c(-996), NA, snapnowadmin),
    
    # Create participation classification
    snap_participation = case_when(
      matchconsenthh == 1 & snapnowadmin == 1 ~ "Participant (Admin confirmed)",
      matchconsenthh == 1 & snapnowadmin == 2 ~ "Nonparticipant (Admin confirmed)",
      matchconsenthh == 1 & snapnowadmin == 0 ~ "Attempted match, no participation",
      matchconsenthh == 0 & snapnowhh == 1 ~ "Participant (Self-report, no consent)",
      matchconsenthh == 0 & snapnowhh == 0 ~ "Nonparticipant (Self-report, no consent)",
      TRUE ~ "Unknown"
    ),
    
    # Food security
    foodsec_low = case_when(
      adltfscat == 3 ~ 1,  # Low food security
      TRUE ~ 0
    ),
    foodsec_verylow = case_when(
      adltfscat == 4 ~ 1,  # Very low food security
      TRUE ~ 0
    ),
    
    # Sex
    Female = case_when(
      SEX == 2 ~ 1,
      SEX == 1 ~ 0,
      TRUE ~ NA_real_
    ),
    
    # Race indicators
    race_white = ifelse(RACECAT_R == 1, 1, 0),
    race_black = ifelse(RACECAT_R == 2, 1, 0),
    race_other = ifelse(RACECAT_R %in% c(3,4,5,6), 1, 0),
    
    # Marital status
    marital_married = ifelse(MARITAL == 1, 1, 0),
    marital_formerly = ifelse(MARITAL %in% c(2,3,4), 1, 0),
    marital_never = ifelse(MARITAL == 5, 1, 0),
    
    # Education
    edu_less_hs = ifelse(EDUCCAT %in% c(1,2), 1, 0),
    edu_hs = ifelse(EDUCCAT == 3, 1, 0),
    edu_some_college = ifelse(EDUCCAT == 4, 1, 0),
    edu_college_plus = ifelse(EDUCCAT %in% c(5,6), 1, 0),
    
    # SNAP-authorized store indicator
    primstore_snapauth = case_when(
      primstoresnaptype == "BC" ~ 0,              # Not SNAP authorized
      is.na(primstoresnaptype) ~ NA_real_,        # Missing
      TRUE ~ 1), 
    
    # Employment
    worked_last_week = case_when(
      EMPLOYMENT %in% c(1,2,3) ~ 1,
      EMPLOYMENT %in% c(4,5) ~ 0,
      EMPLOYMENT %in% c(-996,-998,-997) ~ NA_real_
    ))


```


```{r}
design_t2 <- svydesign(
  ids    = ~tspsu,
  strata = ~tsstrata,
  weights= ~hhwgt,
  nest   = TRUE,
  data   = Table_2_data_frame
)
```


```{r}
library(stargazer)

# Weighted counts
weighted_counts <- svytable(~ snap_participation, design = design_t2)
weighted_pct <- prop.table(weighted_counts) * 100




# Weighted percentages
weighted_pct_df <- data.frame(
  Category = names(weighted_pct),
  Percent = round(as.numeric(weighted_pct), 1)
)

# Use stargazer to make a table
p <- stargazer(weighted_pct_df, type = "text", summary = FALSE, rownames = FALSE)


```

```{r}


Table3_sample <- Table_2_data_frame %>%
  mutate(
    snapnowadmin = ifelse(snapnowadmin %in% c(-996), NA, snapnowadmin),
    snapnowhh = ifelse(snapnowhh %in% c(-997), NA, snapnowhh)
  )

# Weighted participation rate using SNAP_ADMIN
admin_rate <- svymean(~ snapnowadmin, design = design_t2, na.rm = TRUE) * 100

# Weighted participation rate using SNAP_HH (EBT/ALERT)
ebt_rate <- svymean(~ snapnowhh, design = design_t2, na.rm = TRUE) * 100

# Combine into a data frame for Table 3
Table3_summary <- data.frame(
  Measure = c("Admin match (SNAP_ADMIN)", "EBT transactions (SNAP_HH)"),
  Percent = round(c(admin_rate, ebt_rate), 1)
)
```


```{r}
stargazer(Table3_summary, type = "text", summary = FALSE, rownames = FALSE)
```






