---
title: "AFRE 891 - Project Replication"
date: "2025-11-30"
output:
  html_document:
    theme: "journal"
    toc: true
    toc_float: true
    number_sections: false
---



```{r include=FALSE}
library(tidyverse)
library(survey)
library(kableExtra)
library(stargazer)
library(fixest)
library(modelsummary)
```

```{r include=FALSE}
#Files Needed:
household<- read_csv("~/GitHub/AFRE_Project_Rahman/Raw_Data/faps_household_puf.csv")
Individual<- read_csv("~/GitHub/AFRE_Project_Rahman/Raw_Data/faps_individual_puf.csv")
fahNutrient <- read_csv("~/GitHub/AFRE_Project_Rahman/Raw_Data/faps_fahnutrients.csv")
fafHNutrient <- read_csv("~/GitHub/AFRE_Project_Rahman/Raw_Data/faps_fafhnutrient_puf.csv")
faps_fahitem <- read_csv("~/GitHub/AFRE_Project_Rahman/Raw_Data/faps_fahitem_puf.csv")
faps_fafhitem <- read_csv("~/GitHub/AFRE_Project_Rahman/Raw_Data/faps_fafhitem_puf.csv")
```

# This project replicates the main analyses of Courtemanche et al. (2019) using the public-use FoodAPS data.
 https://onlinelibrary.wiley.com/doi/10.1002/soej.12364

# Table 1: Data Preparation and Variable Reconstruction

```{r}
# Prepare household-level variables
household_1 <- household %>%
  select(
    hhnum,
    snapnowreport,
    snapnowadmin,
    snapnowhh,
    matchconsenthh,
    adltfsraw,
    adltfscat,
    pctpovguidehh_r,
    hhwgt,
    tspsu,
    tsstrata,
    hhsize,
    rural,
    inchhavg_r,
    primstoredist_d,
    primstoresnaptype
  )

# Prepare individual-level variables
Individual_1 <- Individual %>%
  select(
    HHNUM,
    BMI,
    SEX,
    RACECAT_R,
    MARITAL,
    EMPLOYMENT,
    EDUCCAT,
    AGE_R
  ) %>%
  rename(hhnum = HHNUM)

```

## Table Construction and Handling Missing and Masked Values

To construct Table 1, I merged the household, individual, and nutrient files from the FoodAPS PUF and recreated every analytic variable used by Courtemanche et al. (2019). Since the PUF omits several restricted-use fields, I had to:

<ol>
<li>Rebuild all household composition indicators (children under 5, elderly, number of children)</li>
<li>Generate dummy variables for race, marital status, education, employment, and store authorization</li>
<li>Recode masked values (−996, −997, −998) as missing</li>
<li>Reconstruct the HEI-2010 from FAH and FAFH nutrient </li>
</ol>

Binary indicators such as Female, Obese, Rural, and Worked last week follow simple 0/1 definitions (e.g., Female = 1 for women). This allows me to compute survey-weighted population shares.

Because the HEI score is not included in the PUF, I calculated it manually following USDA scoring rules. This introduces some measurement error relative to the restricted files used by the authors.

After preparing the analytic dataset, I applied the complex FoodAPS survey design (PSUs, strata, and household weights) and calculated weighted means and standard errors. My results follow the structure of Courtemanche et al. (2019), though some estimates differ due to PUF masking and HEI reconstruction.

```{r}
# Aggregate household-level age variables
children_elderly <- Individual_1 %>%
  group_by(hhnum) %>%
  summarise(
    Number_of_children = sum(AGE_R < 18, na.rm = TRUE),
    child_lt5 = as.numeric(sum(AGE_R < 5, na.rm = TRUE) > 0),
    elderly_65 = as.numeric(sum(AGE_R >= 65, na.rm = TRUE) > 0),
    .groups = "drop"
  )

# Merge household + individual + aggregated household-level age variables
Table_1_data_frame <- household_1 %>%
  left_join(Individual_1, by = "hhnum") %>%
  left_join(children_elderly, by = "hhnum") %>%
  mutate(
    # BMI / Obesity
    Obese = ifelse(BMI >= 30, 1, 0),
    Severely_Obese = ifelse(BMI >= 35, 1, 0),
    
    # SNAP
    SNAP_REPORT = ifelse(snapnowreport %in% c(0,1), snapnowreport, NA),
    SNAP_ADMIN = ifelse(snapnowadmin %in% c(0,1), snapnowadmin, NA),
    SNAP_HH = ifelse(snapnowhh %in% c(0,1), snapnowhh, NA),
    
    # Food security
    foodsec_low = case_when(
      adltfscat == 3 ~ 1,  # Low food security
      TRUE ~ 0
    ),
    foodsec_verylow = case_when(
      adltfscat == 4 ~ 1,  # Very low food security
      TRUE ~ 0
    ),
    
    # Sex
    Female = case_when(
      SEX == 2 ~ 1,
      SEX == 1 ~ 0,
      TRUE ~ NA_real_
    ),
    
    # Race indicators
    race_white = ifelse(RACECAT_R == 1, 1, 0),
    race_black = ifelse(RACECAT_R == 2, 1, 0),
    race_other = ifelse(RACECAT_R %in% c(3,4,5,6), 1, 0),
    
    # Marital status
    marital_married = ifelse(MARITAL == 1, 1, 0),
    marital_formerly = ifelse(MARITAL %in% c(2,3,4), 1, 0),
    marital_never = ifelse(MARITAL == 5, 1, 0),
    
    # Education
    edu_less_hs = ifelse(EDUCCAT %in% c(1,2), 1, 0),
    edu_hs = ifelse(EDUCCAT == 3, 1, 0),
    edu_some_college = ifelse(EDUCCAT == 4, 1, 0),
    edu_college_plus = ifelse(EDUCCAT %in% c(5,6), 1, 0),
    
    # SNAP-authorized store indicator
    primstore_snapauth = case_when(
      primstoresnaptype == "BC" ~ 0,              # Not SNAP authorized
      is.na(primstoresnaptype) ~ NA_real_,        # Missing
      TRUE ~ 1), 
    
    # Employment
    worked_last_week = case_when(
      EMPLOYMENT %in% c(1,2,3) ~ 1,
      EMPLOYMENT %in% c(4,5) ~ 0,
      EMPLOYMENT %in% c(-996,-998,-997) ~ NA_real_
    ))

```

## Construct The HEI

Because the FoodAPS PUF does not include HEI-2010 scores, I reconstructed them using the FAH and FAFH item-level nutrient files. The USDA guidance recommends selecting edible-weight variables in a specific order; I followed this using coalesce() to ensure each item receives the best available gram-weight measure.

I then merged the nutrient and item files, combined FAH and FAFH purchases, and aggregated nutrients to the household level. HEI components require density measures (e.g., cups per 1000 kcal, grams per 1000 kcal, fatty acid ratios, percent of calories from solid fats and added sugars), so I converted everything to per-1000-kcal units before applying USDA scoring cutoffs.

This reconstruction follows the HEI-2010 methodology closely but cannot perfectly match the restricted HEI variables available to the original authors. As a result, my HEI distribution has slightly higher variance, and coefficients in later regressions differ somewhat from the published results.

Reference: https://ers.usda.gov/sites/default/files/_laserfiche/publications/87013/TB-1947.pdf?v=18216 

```{r}
fah_item_hei <- faps_fahitem
Fafh_item_hei <- faps_fafhitem
fah_nutrient_hei <- fahNutrient
fafh_nutrient_hei <- fafHNutrient

```

```{r}

fah_item_hei <- fah_item_hei %>%
  mutate(
    grams_edible = coalesce(
      "totgramsedible",
      "totgramsedibleimp",
      "totgramsunadj",
      "totgramsunadjimp"
    )
  )

```

```{r}

fah_nutrient_hei <- fah_nutrient_hei %>%
  mutate(
    grams_edible = coalesce(
      "totgramsedible",
      "totgramsedibleimp",
      "totgramsunadj",
      "totgramsunadjimp"
    )
  )


```


```{r}
fah_full_hei <- fah_nutrient_hei %>%
  left_join(fah_item_hei, by = c("hhnum","eventid","itemnum"))
```


```{r}
Fafh_item_hei <- Fafh_item_hei %>%
  mutate(
    grams_edible = coalesce(
      "totgramsedible",
      "totgramsedibleimp",
      "totgramsunadj",
      "totgramsunadjimp"
    )
  )

```

```{r}
fafh_nutrient_hei <- fafh_nutrient_hei %>%
  mutate(
    grams_edible = coalesce(
      "totgramsedible",
      "totgramsedibleimp",
      "totgramsunadj",
      "totgramsunadjimp"
    )
  )

```

```{r}
fafh_full_hei <- fafh_nutrient_hei %>%
  left_join(Fafh_item_hei, by = c("hhnum","eventid","itemnum"))
```


```{r}
HEI_ALL <- bind_rows(
  fah_full_hei %>% mutate(source = "FAH"),
  fafh_full_hei %>% mutate(source = "FAFH")
)
```


```{r}
HEI_ALL <- HEI_ALL %>%
  group_by(hhnum) %>%
  summarise(
    energy     = sum(energy, na.rm = TRUE),

    # Dairy
    d_total    = sum(d_total, na.rm = TRUE),

    # Fruits
    f_total    = sum(f_total, na.rm = TRUE),
    f_whole    = sum(f_other, na.rm = TRUE),
    f_juice    = sum(f_juice, na.rm = TRUE),

    # Vegetables
    v_total    = sum(v_total, na.rm = TRUE),
    v_dark     = sum(v_drkgr, na.rm = TRUE),
    v_legumes  = sum(v_legumes, na.rm = TRUE),

    # Grains
    g_whole    = sum(g_whole, na.rm = TRUE),
    g_refined  = sum(g_refined, na.rm = TRUE),

    # Proteins
    pf_total   = sum(pf_total, na.rm = TRUE),
    pf_plant   = sum(pf_soy + pf_nutsds + pf_legumes, na.rm = TRUE),
    pf_seafood = sum(pf_seafd_hi + pf_seafd_low, na.rm = TRUE),

    # Fatty acids
    satfat     = sum(satfat, na.rm = TRUE),
    monofat    = sum(monofat, na.rm = TRUE),
    polyfat    = sum(polyfat, na.rm = TRUE),

    # Sodium / empty calories
    sodium     = sum(sodium, na.rm = TRUE),
    solid_fats = sum(solid_fats, na.rm = TRUE),
    add_sugars = sum(add_sugars, na.rm = TRUE)
  )

```
.

```{r}
hei_components <- HEI_ALL %>%
  mutate(
    kcal1000 = energy / 1000,

    # HEI-2010 per 1000 kcal components
    fruit_total     = f_total / kcal1000,
    fruit_whole     = f_whole / kcal1000,
    veg_total       = v_total / kcal1000,
    greens_beans    = (v_dark + v_legumes) / kcal1000,

    whole_grains    = g_whole / kcal1000,
    dairy_comp      = d_total / kcal1000,

    protein_total   = pf_total / kcal1000,
    seaplant        = (pf_plant + pf_seafood) / kcal1000,

    fatty_acid_ratio = (monofat + polyfat) / satfat,

    # Moderation (lower = better)
    sodium_kcal      = sodium / kcal1000,
    refined_grains   = g_refined / kcal1000,

    # Empty calories (percentage of total kcal)
    pct_empty = 100 * (
      solid_fats*9 + add_sugars*4
    ) / energy
  )

```

```{r}
hei_scores <- hei_components %>%
  mutate(

    score_totfruit     = pmin(5,  fruit_total     / 0.8),
    score_wholefruit   = pmin(5,  fruit_whole     / 0.4),
    score_totalveg     = pmin(5,  veg_total       / 1.1),
    score_greensbeans  = pmin(5,  greens_beans    / 0.2),

    score_wholegrains  = pmin(10, whole_grains    / 1.5),
    score_dairy        = pmin(10, dairy_comp      / 1.3),

    score_protein      = pmin(5,  protein_total   / 2.5),
    score_seaplant     = pmin(5,  seaplant        / 0.8),

    score_fattyacid    = pmin(10, fatty_acid_ratio / 2.5),

    score_sodium  = pmax(0, 10 * ( (2.0 - sodium_kcal) / (2.0 - 1.1) )),
    score_refined = pmax(0, 10 * ( (4.3 - refined_grains) / (4.3 - 1.8) )),

    score_empty   = pmax(0, 20 * ( (50 - pct_empty) / (50 - 19) )),

    hei_total = rowSums(across(starts_with("score_")))
  )

```


```{r}
HEI_Total <- hei_scores %>%
  select(hhnum, hei_total)

Table_1_data_frame <- Table_1_data_frame %>%
  left_join(HEI_Total, by = "hhnum")
```


## TABLE 1 — Design
To prepare Table 1, I first converted all variables to numeric form and removed a store-type string variable that I had already recoded. I restricted the sample to households that consented to SNAP administrative matching and had income below 250% of the poverty guideline, mirroring the sample used in the original study. I then required complete data for all analytic variables.


```{r}
Table1_sample <- Table_1_data_frame %>%
   mutate(
    across(
    everything(), 
    ~ as.numeric(.))) %>%
  select(-primstoresnaptype) %>%
  filter(matchconsenthh == 1) %>%
  filter(pctpovguidehh_r <= 250)%>%
  filter(if_all(
    .cols = c(
      1:46 # store SNAP authorized
    ),
    ~!is.na(.)
  )) %>%
  distinct(hhnum, .keep_all = TRUE)
```

After defining the  survey design with sampling weights, strata, and PSUs, I computed weighted means and standard errors for each variable using the survey package. My table replicates the structure and logic of Courtemanche et al. (2019), though some estimates necessarily differ because I used only public-use FoodAPS data and constructed the HEI scores manually.: https://stats.oarc.ucla.edu/r/seminars/survey-data-analysis-with-r/ 

```{r}

design_t1 <- svydesign(
  ids    = ~tspsu,
  strata = ~tsstrata,
  weights= ~hhwgt,
  nest   = TRUE,
  data   = Table1_sample
)
```



```{r}
svy_mean_foodsec_low <- svymean(~foodsec_low, design_t1, na.rm = TRUE)
```


```{r}
svy_mean_fmt <- function(var, design_t1, label) {
  res <- svymean(as.formula(paste("~", var)), design_t1, na.rm = TRUE)
  mean_val <- as.numeric(res)
  se_val <- as.numeric(SE(res))
  data.frame(
    Variable = label,
    Mean_SE = paste0(round(mean_val, 2), " (", round(se_val, 2), ")"),
    stringsAsFactors = FALSE
  )
}
```

These next lines of code are to make the table below
```{r}
table1_list <- list(
  # SNAP participation
  svy_mean_fmt("SNAP_REPORT", design_t1, "Self-reported (REPORT)"),
  svy_mean_fmt("SNAP_ADMIN", design_t1, "Administrative from caseload data (ADMIN)"),
  svy_mean_fmt("SNAP_HH", design_t1, "Administrative from EBT transactions (ALERT)"),
  
  # Dependent variables
  svy_mean_fmt("foodsec_low", design_t1, "Low food security"),
  svy_mean_fmt("foodsec_verylow", design_t1, "Very low food security"),
  svy_mean_fmt("hei_total", design_t1, "Total 2010 HEI score"),
  svy_mean_fmt("BMI", design_t1, "Body mass index"),
  svy_mean_fmt("Obese", design_t1, "Obese"),
  svy_mean_fmt("Severely_Obese", design_t1, "Severely obese"),
  
  # Control variables
  svy_mean_fmt("AGE_R", design_t1, "Age (years)"),
  svy_mean_fmt("Female", design_t1, "Female"),
  svy_mean_fmt("race_black", design_t1, "Black"),
  svy_mean_fmt("race_white", design_t1, "White"),
  svy_mean_fmt("race_other", design_t1, "Other race (non-black, non-white)"),
  svy_mean_fmt("marital_married", design_t1, "Married"),
  svy_mean_fmt("marital_formerly", design_t1, "Formerly married"),
  svy_mean_fmt("hhsize", design_t1, "Household size"),
  svy_mean_fmt("Number_of_children", design_t1, "Number of children"),
  svy_mean_fmt("rural", design_t1, "Rural tract"),
  svy_mean_fmt("edu_less_hs", design_t1, "Less than high school education"),
  svy_mean_fmt("edu_hs", design_t1, "High school graduate"),
  svy_mean_fmt("edu_some_college", design_t1, "Some college education"),
  svy_mean_fmt("edu_college_plus", design_t1, "College degree or higher"),
  svy_mean_fmt("worked_last_week", design_t1, "Worked last week"),
  svy_mean_fmt("pctpovguidehh_r", design_t1, "Gross monthly family income ($1000s)"),
  svy_mean_fmt("child_lt5", design_t1, "Child less than five years present in HH"),
  svy_mean_fmt("elderly_65", design_t1, "Elderly at least 65 years present in HH"),
  svy_mean_fmt("marital_never", design_t1, "Never married"),
  svy_mean_fmt("primstoredist_d", design_t1, "Miles from residence to primary food store"),
  svy_mean_fmt("primstore_snapauth", design_t1, "Primary food store is SNAP-authorized")
)

Table1_summary <- bind_rows(table1_list)

```


```{r}

snap_vars <- c("Self-reported (REPORT)",
               "Administrative from caseload data (ADMIN)",
               "Administrative from EBT transactions (ALERT)")

dep_vars <- c("Low food security",
              "Very low food security",
              "Total 2010 HEI score",
              "Body mass index",
              "Obese",
              "Severely obese")

control_vars <- c("Age (years)",
                  "Female",
                  "Black",
                  "White",
                  "Other race (non-black, non-white)",
                  "Married",
                  "Formerly married",
                  "Household size",
                  "Number of children",
                  "Rural tract",
                  "Less than high school education",
                  "High school graduate",
                  "Some college education",
                  "College degree or higher",
                  "Worked last week",
                  "Gross monthly family income ($1000s)",
                  "Child less than five years present in HH",
                  "Elderly at least 65 years present in HH",
                  "Never married",
                  "Miles from residence to primary food store",
                  "Primary food store is SNAP-authorized")

snap_summary <- Table1_summary %>% filter(Variable %in% snap_vars)
dep_summary <- Table1_summary %>% filter(Variable %in% dep_vars)
control_summary <- Table1_summary %>% filter(Variable %in% control_vars)

header_snap <- data.frame(Variable = "SNAP participation", Mean_SE = "", stringsAsFactors = FALSE)
header_dep <- data.frame(Variable = "Dependent variables", Mean_SE = "", stringsAsFactors = FALSE)
header_control <- data.frame(Variable = "Control variables", Mean_SE = "", stringsAsFactors = FALSE)

Table1_final <- bind_rows(
  header_snap, snap_summary,
  header_dep, dep_summary,
  header_control, control_summary
)




```

Table output reference: https://bookdown.org/yihui/rmarkdown-cookbook/kableextra.html 
```{r}


Table1_final_indented <- Table1_final %>%
  mutate(
    Variable = ifelse(
      Mean_SE != "",                    
      paste0("&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;", Variable),  
      Variable                          
    )
  )

# Render table
Table_1_Rendered <- Table1_final_indented %>%
  kable(format = "html", escape = FALSE, col.names = c("Variable", "Mean (SE)")) %>%
  kable_styling(
    full_width = TRUE,
    bootstrap_options = c("striped", "hover")
  ) %>%
  add_header_above(c("Table 1. Summary Statistics" = 2), align = "left") %>%
  footnote(
    general = "Notes: Statistics are from main sample. Means and standard errors are survey-weighted."
  )

```

```{r}
Table_1_Rendered
```



# TABLE 2 — SNAP Participation Classification
Table 2 classifies households by SNAP participation using three PUF variables—SNAPNOWREPORT, SNAPNOWADMIN, and SNAPNOWHH—along with match consent (MATCHCONSENTHH). Unlike the restricted files, the PUF masks match quality, benefit-month history, and some administrative outcomes. Because of this, I construct the categories using simplified binary logic.

## Here is the classification
<ul>
  <li>Self-report (SNAPNOWREPORT)
    <ul>
      <li>1 = household reports receiving SNAP</li>
      <li>0 = household reports no SNAP</li>
      <li>−997/−998 = “don’t know/refused” → set to NA</li>
    </ul>
  </li>

  <li>Administrative match (SNAPNOWADMIN)
    <ul>
      <li>1 = admin confirms participation</li>
      <li>2 = admin confirms nonparticipation → recoded as 0</li>
      <li>0 = no match (ambiguous: nonparticipant or match failure)</li>
      <li>−996 = no consent → set to NA</li>
    </ul>
  </li>

  <li>Match consent (MATCHCONSENTHH)
    <ul>
      <li>1 = admin data should be available</li>
      <li>0 = no matching allowed → cannot use SNAPNOWADMIN</li>
    </ul>
  </li>

  <li>For consenting households (MATCHCONSENTHH = 1), classify:
    <ul>
      <li>Admin-confirmed participant (admin = 1)</li>
      <li>Admin-confirmed nonparticipant (admin = 2 → 0)</li>
      <li>Attempted match / no participation (admin = 0)</li>
    </ul>
  </li>
</ul>

For nonconsenting households, I rely on SNAPNOWHH, which blends admin and self-report information in the PUF.

Because the PUF collapses “no match” and “confirmed nonparticipation” into the same value (0), my categories necessarily differ from those in the restricted data used by Courtemanche et al.


```{r}
# Prepare household-level variables
household_2 <- household %>%
  select(
    hhnum,
    snapnowreport,
    snapnowadmin,
    snapnowhh,
    matchconsenthh,
    adltfsraw,
    adltfscat,
    pctpovguidehh_r,
    hhwgt,
    tspsu,
    tsstrata,
    hhsize,
    rural,
    inchhavg_r,
    primstoredist_d,
    primstoresnaptype
  )

# Prepare individual-level variables
Individual_2 <- Individual %>%
  select(
    HHNUM,
    BMI,
    SEX,
    RACECAT_R,
    MARITAL,
    EMPLOYMENT,
    EDUCCAT,
    AGE_R
  ) %>%
  rename(hhnum = HHNUM)
```

```{r}
# Aggregate household-level age variables
children_elderly <- Individual_2 %>%
  group_by(hhnum) %>%
  summarise(
    Number_of_children = sum(AGE_R < 18, na.rm = TRUE),
    child_lt5 = as.numeric(sum(AGE_R < 5, na.rm = TRUE) > 0),
    elderly_65 = as.numeric(sum(AGE_R >= 65, na.rm = TRUE) > 0),
    .groups = "drop"
  )

```


```{r}

# Merge household + individual + aggregated household-level age variables
Table_2_data_frame <- household_2 %>%
  left_join(Individual_2, by = "hhnum") %>%
  left_join(children_elderly, by = "hhnum") %>%
  mutate(
    # BMI / Obesity
    Obese = ifelse(BMI >= 30, 1, 0),
    Severely_Obese = ifelse(BMI >= 35, 1, 0),
      # Set NA for “don’t know/refused” codes
    snapnowhh = ifelse(snapnowhh %in% c(-997), NA, snapnowhh),
    snapnowreport = ifelse(snapnowreport %in% c(-997, -998), NA, snapnowreport),
    snapnowadmin = ifelse(snapnowadmin %in% c(-996), NA, snapnowadmin),
    
    # Create participation classification
    snap_participation = case_when(
      matchconsenthh == 1 & snapnowadmin == 1 ~ "Participant (Admin confirmed)",
      matchconsenthh == 1 & snapnowadmin == 2 ~ "Nonparticipant (Admin confirmed)",
      matchconsenthh == 1 & snapnowadmin == 0 ~ "Attempted match, no participation",
      matchconsenthh == 0 & snapnowhh == 1 ~ "Participant (Self-report, no consent)",
      matchconsenthh == 0 & snapnowhh == 0 ~ "Nonparticipant (Self-report, no consent)",
      TRUE ~ "Unknown"
    ),
    
    # Food security
    foodsec_low = case_when(
      adltfscat == 3 ~ 1,  # Low food security
      TRUE ~ 0
    ),
    foodsec_verylow = case_when(
      adltfscat == 4 ~ 1,  # Very low food security
      TRUE ~ 0
    ),
    
    # Sex
    Female = case_when(
      SEX == 2 ~ 1,
      SEX == 1 ~ 0,
      TRUE ~ NA_real_
    ),
    
    # Race indicators
    race_white = ifelse(RACECAT_R == 1, 1, 0),
    race_black = ifelse(RACECAT_R == 2, 1, 0),
    race_other = ifelse(RACECAT_R %in% c(3,4,5,6), 1, 0),
    
    # Marital status
    marital_married = ifelse(MARITAL == 1, 1, 0),
    marital_formerly = ifelse(MARITAL %in% c(2,3,4), 1, 0),
    marital_never = ifelse(MARITAL == 5, 1, 0),
    
    # Education
    edu_less_hs = ifelse(EDUCCAT %in% c(1,2), 1, 0),
    edu_hs = ifelse(EDUCCAT == 3, 1, 0),
    edu_some_college = ifelse(EDUCCAT == 4, 1, 0),
    edu_college_plus = ifelse(EDUCCAT %in% c(5,6), 1, 0),
    
    # SNAP-authorized store indicator
    primstore_snapauth = case_when(
      primstoresnaptype == "BC" ~ 0,              # Not SNAP authorized
      is.na(primstoresnaptype) ~ NA_real_,        # Missing
      TRUE ~ 1), 
    
    # Employment
    worked_last_week = case_when(
      EMPLOYMENT %in% c(1,2,3) ~ 1,
      EMPLOYMENT %in% c(4,5) ~ 0,
      EMPLOYMENT %in% c(-996,-998,-997) ~ NA_real_
    ))


```


```{r}
design_t2 <- svydesign(
  ids    = ~tspsu,
  strata = ~tsstrata,
  weights= ~hhwgt,
  nest   = TRUE,
  data   = Table_2_data_frame
)
```

My participation distribution differs from the paper because:
Admin = 0 sometimes means “not matched,” not “not participating”
self-report has noisier coding in PUFs
I cannot identify partial month participation

```{r}

# Weighted counts
weighted_counts <- svytable(~ snap_participation, design = design_t2)
weighted_pct <- prop.table(weighted_counts) * 100




# Weighted percentages
weighted_pct_df <- data.frame(
  Category = names(weighted_pct),
  Percent = round(as.numeric(weighted_pct), 1)
)

# Use stargazer to make a table
p <- stargazer(weighted_pct_df, type = "text", summary = FALSE, rownames = FALSE)


```



# Table 3
Table 3 reports survey-weighted SNAP participation using two PUF measures:

SNAP_ADMIN — the administrative match

SNAP_HH — a hybrid measure combining admin and self-report

<ul>
  <li>SNAPNOWADMIN (PUF)
    <ul>
      <li>1 = confirmed participant</li>
      <li>2 = confirmed nonparticipant</li>
      <li>0 = unmatched (may be true nonparticipant or match failure)</li>
      <li>−996 = no consent → removed</li>
    </ul>
  </li>

  <li>Recode to SNAP_ADMIN (0/1)
    <ul>
      <li>1 = admin-participant</li>
      <li>0 = nonparticipant or unmatched</li>
    </ul>
  </li>
</ul>

SNAP_HH is a composite constructed by USDA: if the household consents, it uses admin data; otherwise it uses self-report. This is not equivalent to the ALERT transaction data used in the restricted files.

Because unmatched cases are coded as 0 in the PUF, the administrative participation rate is slightly understated relative to the original paper.

```{r}


Table3_sample <- Table_2_data_frame %>%
  mutate(
    snapnowadmin = ifelse(snapnowadmin %in% c(-996), NA, snapnowadmin),
    snapnowhh = ifelse(snapnowhh %in% c(-997), NA, snapnowhh)
  )

# Weighted participation rate using SNAP_ADMIN
admin_rate <- svymean(~ snapnowadmin, design = design_t2, na.rm = TRUE) * 100

# Weighted participation rate using SNAP_HH (EBT/ALERT)
ebt_rate <- svymean(~ snapnowhh, design = design_t2, na.rm = TRUE) * 100

# Combine into a data frame for Table 3
Table3_summary <- data.frame(
  Measure = c("Admin match (SNAP_ADMIN)", "EBT transactions (SNAP_HH)"),
  Percent = round(c(admin_rate, ebt_rate), 1)
)
```


```{r}
stargazer(Table3_summary, type = "text", summary = FALSE, rownames = FALSE)
```



# Table 4
Table 4 compares self-reported and administrative SNAP participation to measure misreporting. Because I use the PUF, which has a simplified administrative variable, my classification is an approximation of the original paper’s method.

I restrict the sample to households that consented to matching and have income below 250% of poverty. I then construct four mutually exclusive indicators:

<ul>
  <li>Classification (self-report vs. admin)
    <ul>
      <li>True Positive (1/1): self-report = 1 and admin = 1</li>
      <li>True Negative (0/0): self-report = 0 and admin = 0 or 2</li>
      <li>False Negative (0/1): under-reporting (admin = 1, report = 0)</li>
      <li>False Positive (1/0): over-reporting (admin = 0 or 2, report = 1)</li>
    </ul>
  </li>

  <li>PUF considerations (admin = 0 ambiguity)
    <ul>
      <li>Admin = 0 includes true nonparticipants and unmatched cases</li>
      <li>True negatives are inflated</li>
      <li>False positives absorb some match failures</li>
      <li>False negatives are sensitive to admin under-coverage</li>
    </ul>
  </li>

  <li>Computed metrics (weighted)
    <ul>
      <li>Under-reporting rate: FN / admin participation</li>
      <li>Over-reporting rate: FP / (1 − admin participation)</li>
      <li>Total misreporting: FN + FP</li>
    </ul>
  </li>
</ul>

These measures follow the structure of the original paper but differ in level because the PUF does not distinguish failed matches from confirmed nonparticipation.

```{r}

Table4_sample <- Table_1_data_frame %>%
  filter(
    matchconsenthh == 1,
    pctpovguidehh_r <= 250
  ) %>%
  distinct(hhnum, .keep_all = TRUE)
```


```{r}
design_t4 <- svydesign(
  ids = ~tspsu,
  strata = ~tsstrata,
  weights = ~hhwgt,
  nest = TRUE,
  data = Table4_sample
)
```


```{r}

Table4_sample <- Table4_sample %>%
  mutate(
    true_pos  = as.numeric(snapnowreport == 1 & snapnowadmin == 1),
    true_neg  = as.numeric(snapnowreport == 0 & snapnowadmin == 0),
    false_neg = as.numeric(snapnowreport == 0 & snapnowadmin == 1),
    false_pos = as.numeric(snapnowreport == 1 & snapnowadmin == 0),
    misrep    = as.numeric(false_neg == 1 | false_pos == 1) 
  )

design_t4 <- update(design_t4, 
                    true_pos  = Table4_sample$true_pos,
                    true_neg  = Table4_sample$true_neg,
                    false_neg = Table4_sample$false_neg,
                    false_pos = Table4_sample$false_pos)


admin_part     <- svymean(~snapnowadmin, design_t4)[1]
tp_rate        <- svymean(~true_pos, design_t4)[1]
tn_rate        <- svymean(~true_neg, design_t4)[1]
fn_rate        <- svymean(~false_neg, design_t4)[1]
fp_rate        <- svymean(~false_pos, design_t4)[1]

under_report   <- fn_rate / admin_part
over_report    <- fp_rate / (1 - admin_part)
total_misrep   <- fn_rate + fp_rate




```

```{r}
Table4_df <- data.frame(
  Measure = c(
    "SNAP Participation (Admin)",
    "True Positives (1/1)",
    "True Negatives (0/0)",
    "False Negatives (0/1)",
    "False Positives (1/0)",
    "Under-reporting Rate",
    "Over-reporting Rate",
    "Total Misreporting"
  ),
  Value = round(
    c(
      admin_part,
      tp_rate,
      tn_rate,
      fn_rate,
      fp_rate,
      under_report,
      over_report,
      total_misrep
    ) * 100, 2)
)



```

```{r}
 stargazer(
  Table4_df,
  type = "text",            # change to "latex" or "html" as needed
  summary = FALSE,
  rownames = FALSE,
  title = "Table 4: SNAP Reporting Measures",
  digits = 2,
  column.labels = c("Measure", "Value (%)")
)

```


# Tables 5 and 6 cant be replicated using alternatives


# Table 7
Tables 7 and 8 estimate the association between SNAP participation (and misreporting categories) and a set of health and nutrition outcomes. Unlike Courtemanche et al. (2019), I rely entirely on PUF variables:

<ul>
  <li>SNAP_REPORT — self-reported participation</li>
  <li>SNAP_ADMIN — admin match (masked; admin = 0 conflates “no” and “unmatched”)</li>
  <li>SNAP_HH — hybrid measure combining admin and self-report</li>
</ul>

Because the PUF lacks verified administrative histories, match-quality metrics, and benefit-month timing, all three measures contain noise. Measurement error is especially important for HEI, because I had to reconstruct HEI scores from raw nutrient files. This increases outcome variability and reduces statistical precision.




## Control Variables and Main Effects
```{r}

controls <- "AGE_R + Female + race_white + race_black + race_other +
             marital_married + marital_formerly + marital_never +
             hhsize + Number_of_children + rural +
             edu_less_hs + edu_hs + edu_some_college + edu_college_plus +
             worked_last_week + inchhavg_r + child_lt5 + elderly_65"

snap_rep  <- "SNAP_REPORT"
snap_adm  <- "SNAP_ADMIN"
snap_hh   <- "SNAP_HH"
```


```{r}
my_formula_lm <- function(y, snapvar) {
  as.formula(paste0(y, " ~ ", snapvar, " + ", controls))
}
```


## Snap Admin Regressions

```{r include=FALSE}
fs_adm <- feols(as.formula(paste0("foodsec_low ~ ", snap_adm, " + ", controls)),
                data = Table1_sample, weights = ~hhwgt, cluster = ~tspsu)

vlfs_adm <- feols(as.formula(paste0("foodsec_verylow ~ ", snap_adm, " + ", controls)),
                  data = Table1_sample, weights = ~hhwgt, cluster = ~tspsu)

hei_adm <- feols(as.formula(paste0("hei_total ~ ", snap_adm, " + ", controls)),
                 data = Table1_sample, weights = ~hhwgt, cluster = ~tspsu)

bmi_adm <- feols(as.formula(paste0("BMI ~ ", snap_adm, " + ", controls)),
                 data = Table1_sample, weights = ~hhwgt, cluster = ~tspsu)

ob_adm <- feols(as.formula(paste0("Obese ~ ", snap_adm, " + ", controls)),
                data = Table1_sample, weights = ~hhwgt, cluster = ~tspsu)

sob_adm <- feols(as.formula(paste0("Severely_Obese ~ ", snap_adm, " + ", controls)),
                 data = Table1_sample, weights = ~hhwgt, cluster = ~tspsu)

```

```{r}
modelsummary(
  list(
    "Food Low" = fs_adm,
    "Very Low FS" = vlfs_adm,
    "HEI Total" = hei_adm,
    "BMI" = bmi_adm,
    "Obese" = ob_adm,
    "Severely Obese" = sob_adm
  ),
    coef_omit = "^(?!SNAP_).*",   # KEEP ONLY SNAP VARS
  gof_omit = ".*",
  stars = TRUE,
  output = "markdown",
  title = "Table 7a. Associations Using SNAP_Admin"
)
```



## Snap Report Regressions

```{r include=FALSE}
snap_rep <- "SNAP_REPORT"

fs_rep <- feols(
  as.formula(paste0("foodsec_low ~ ", snap_rep, " + ", controls)),
  data = Table1_sample, weights = ~hhwgt, cluster = ~tspsu
)

vlfs_rep <- feols(
  as.formula(paste0("foodsec_verylow ~ ", snap_rep, " + ", controls)),
  data = Table1_sample, weights = ~hhwgt, cluster = ~tspsu
)

hei_rep <- feols(
  as.formula(paste0("hei_total ~ ", snap_rep, " + ", controls)),
  data = Table1_sample, weights = ~hhwgt, cluster = ~tspsu
)

bmi_rep <- feols(
  as.formula(paste0("BMI ~ ", snap_rep, " + ", controls)),
  data = Table1_sample, weights = ~hhwgt, cluster = ~tspsu
)

ob_rep <- feols(
  as.formula(paste0("Obese ~ ", snap_rep, " + ", controls)),
  data = Table1_sample, weights = ~hhwgt, cluster = ~tspsu
)

sob_rep <- feols(
  as.formula(paste0("Severely_Obese ~ ", snap_rep, " + ", controls)),
  data = Table1_sample, weights = ~hhwgt, cluster = ~tspsu
)

```


```{r}
modelsummary(
  list(
    "Food Low" = fs_rep,
    "Very Low FS" = vlfs_rep,
    "HEI Total" = hei_rep,
    "BMI" = bmi_rep,
    "Obese" = ob_rep,
    "Severely Obese" = sob_rep
  ),
    coef_omit = "^(?!SNAP_).*",   # KEEP ONLY SNAP VARS
  gof_omit = ".*",
  stars = TRUE,
  output = "markdown",
  title = "Table 7b. Associations Using SNAP_REPORT"
)
```

## Snap HH Regressions

```{r include=FALSE}

fs_hh <- feols(as.formula(paste0("foodsec_low ~ ", snap_hh, " + ", controls)),
               data = Table1_sample, weights = ~hhwgt, cluster = ~tspsu)

vlfs_hh <- feols(as.formula(paste0("foodsec_verylow ~ ", snap_hh, " + ", controls)),
                 data = Table1_sample, weights = ~hhwgt, cluster = ~tspsu)

hei_hh <- feols(as.formula(paste0("hei_total ~ ", snap_hh, " + ", controls)),
                data = Table1_sample, weights = ~hhwgt, cluster = ~tspsu)

bmi_hh <- feols(as.formula(paste0("BMI ~ ", snap_hh, " + ", controls)),
                 data = Table1_sample, weights = ~hhwgt, cluster = ~tspsu)

ob_hh <- feols(as.formula(paste0("Obese ~ ", snap_hh, " + ", controls)),
               data = Table1_sample, weights = ~hhwgt, cluster = ~tspsu)

sob_hh <- feols(as.formula(paste0("Severely_Obese ~ ", snap_hh, " + ", controls)),
                data = Table1_sample, weights = ~hhwgt, cluster = ~tspsu)

```

```{r}
modelsummary(
  list(
    "Food Low" = fs_hh,
    "Very Low FS" = vlfs_hh,
    "HEI Total" = hei_hh,
    "BMI" = bmi_hh,
    "Obese" = ob_hh,
    "Severely Obese" = sob_hh
  ),
    coef_omit = "^(?!SNAP_).*",   # KEEP ONLY SNAP VARS
  gof_omit = ".*",
  stars = TRUE,
  output = "markdown",
  title = "Table 7c. Associations Using SNAP_HH"
)

```







# Table 8 

For Table 8, I build the misreporting indicators using simple binary comparisons between self-report and admin:

<ul>
  <li>True positive (1/1)</li>
  <li>True negative (0/0 or 2)</li>
  <li>False negative (0/1)</li>
  <li>False positive (1/0 or 2)</li>
  <li>Misreporting (FN or FP)</li>
</ul>

Because admin = 0 in the PUF is ambiguous, these categories differ from those in the restricted files, and misreporting appears higher in my replication.

Despite these limitations, the regression specifications follow the same logic as the original paper: complex survey weights, household-level clustering, and the same set of demographic and socioeconomic controls.

```{r}
# Convert BMI
Table4_sample <- Table4_sample %>%
  mutate(BMI = as.numeric(BMI))

# Separate SNAP classification variables
snap_admin <- "SNAP_ADMIN"
snap_tp    <- "true_pos"
snap_tn    <- "true_neg"
snap_fn    <- "false_neg"
snap_fp    <- "false_pos"
misrep     <- "misrep"

```

## True Positive / True Negative / False Negative / False Positive / Misreporting Regressions

Regressions follow the same structure as above, swapping in the relevant variable (true_pos, true_neg, false_neg, false_pos, misrep)

### SNAP_ADMIN Regressions
```{r include=FALSE}
fs_admin <- feols(as.formula(paste0("foodsec_low ~ ", snap_admin, " + ", controls)),
                  data = Table4_sample, weights = ~hhwgt, cluster = ~tspsu)

vlfs_admin <- feols(as.formula(paste0("foodsec_verylow ~ ", snap_admin, " + ", controls)),
                    data = Table4_sample, weights = ~hhwgt, cluster = ~tspsu)

hei_admin <- feols(as.formula(paste0("hei_total ~ ", snap_admin, " + ", controls)),
                   data = Table4_sample, weights = ~hhwgt, cluster = ~tspsu)

bmi_admin <- feols(as.formula(paste0("BMI ~ ", snap_admin, " + ", controls)),
                   data = Table4_sample, weights = ~hhwgt, cluster = ~tspsu)

ob_admin <- feols(as.formula(paste0("Obese ~ ", snap_admin, " + ", controls)),
                  data = Table4_sample, weights = ~hhwgt, cluster = ~tspsu)

sob_admin <- feols(as.formula(paste0("Severely_Obese ~ ", snap_admin, " + ", controls)),
                   data = Table4_sample, weights = ~hhwgt, cluster = ~tspsu)

```

```{r}
modelsummary(
  list(
    "Food Low"       = fs_admin,
    "Very Low FS"    = vlfs_admin,
    "HEI Total"      = hei_admin,
    "BMI"            = bmi_admin,
    "Obese"          = ob_admin,
    "Severely Obese" = sob_admin
  ),
  coef_map = c("SNAP_ADMIN" = "SNAP Admin"),
  stars = TRUE,
  title = "Table 8a. Regression Results using SNAP_ADMIN",
  output = "markdown",
  fmt = 3,
  gof_omit = ".*"
)
```

### True Positive Regressions
```{r include=FALSE}
fs_tp <- feols(as.formula(paste0("foodsec_low ~ ", snap_tp, " + ", controls)),
               data = Table4_sample, weights = ~hhwgt, cluster = ~tspsu)

vlfs_tp <- feols(as.formula(paste0("foodsec_verylow ~ ", snap_tp, " + ", controls)),
                 data = Table4_sample, weights = ~hhwgt, cluster = ~tspsu)

hei_tp <- feols(as.formula(paste0("hei_total ~ ", snap_tp, " + ", controls)),
                data = Table4_sample, weights = ~hhwgt, cluster = ~tspsu)

bmi_tp <- feols(as.formula(paste0("BMI ~ ", snap_tp, " + ", controls)),
                data = Table4_sample, weights = ~hhwgt, cluster = ~tspsu)

ob_tp <- feols(as.formula(paste0("Obese ~ ", snap_tp, " + ", controls)),
               data = Table4_sample, weights = ~hhwgt, cluster = ~tspsu)

sob_tp <- feols(as.formula(paste0("Severely_Obese ~ ", snap_tp, " + ", controls)),
                data = Table4_sample, weights = ~hhwgt, cluster = ~tspsu)

```

```{r}
modelsummary(
  list(
    "Food Low"       = fs_tp,
    "Very Low FS"    = vlfs_tp,
    "HEI Total"      = hei_tp,
    "BMI"            = bmi_tp,
    "Obese"          = ob_tp,
    "Severely Obese" = sob_tp
  ),
  coef_map = c("true_pos" = "True Positive"),
  stars = TRUE,
  title = "Table 8b. Regression Results using True Positive",
  output = "markdown",
  fmt = 3,
  gof_omit = ".*"
)
```

### True Negative Regressions
```{r include=FALSE}
fs_tn <- feols(as.formula(paste0("foodsec_low ~ ", snap_tn, " + ", controls)),
               data = Table4_sample, weights = ~hhwgt, cluster = ~tspsu)

vlfs_tn <- feols(as.formula(paste0("foodsec_verylow ~ ", snap_tn, " + ", controls)),
                 data = Table4_sample, weights = ~hhwgt, cluster = ~tspsu)

hei_tn <- feols(as.formula(paste0("hei_total ~ ", snap_tn, " + ", controls)),
                data = Table4_sample, weights = ~hhwgt, cluster = ~tspsu)

bmi_tn <- feols(as.formula(paste0("BMI ~ ", snap_tn, " + ", controls)),
                data = Table4_sample, weights = ~hhwgt, cluster = ~tspsu)

ob_tn <- feols(as.formula(paste0("Obese ~ ", snap_tn, " + ", controls)),
               data = Table4_sample, weights = ~hhwgt, cluster = ~tspsu)

sob_tn <- feols(as.formula(paste0("Severely_Obese ~ ", snap_tn, " + ", controls)),
                data = Table4_sample, weights = ~hhwgt, cluster = ~tspsu)

```

```{r}
modelsummary(
  list(
    "Food Low"       = fs_tn,
    "Very Low FS"    = vlfs_tn,
    "HEI Total"      = hei_tn,
    "BMI"            = bmi_tn,
    "Obese"          = ob_tn,
    "Severely Obese" = sob_tn
  ),
  coef_map = c("true_neg" = "True Negative"),
  stars = TRUE,
  title = "Table 8c. Regression Results using True Negative",
  output = "markdown",
  fmt = 3,
  gof_omit = ".*"
)
```


### False Negative Regressions
```{r include=FALSE}
fs_fn <- feols(as.formula(paste0("foodsec_low ~ ", snap_fn, " + ", controls)),
               data = Table4_sample, weights = ~hhwgt, cluster = ~tspsu)

vlfs_fn <- feols(as.formula(paste0("foodsec_verylow ~ ", snap_fn, " + ", controls)),
                 data = Table4_sample, weights = ~hhwgt, cluster = ~tspsu)

hei_fn <- feols(as.formula(paste0("hei_total ~ ", snap_fn, " + ", controls)),
                data = Table4_sample, weights = ~hhwgt, cluster = ~tspsu)

bmi_fn <- feols(as.formula(paste0("BMI ~ ", snap_fn, " + ", controls)),
                data = Table4_sample, weights = ~hhwgt, cluster = ~tspsu)

ob_fn <- feols(as.formula(paste0("Obese ~ ", snap_fn, " + ", controls)),
               data = Table4_sample, weights = ~hhwgt, cluster = ~tspsu)

sob_fn <- feols(as.formula(paste0("Severely_Obese ~ ", snap_fn, " + ", controls)),
                data = Table4_sample, weights = ~hhwgt, cluster = ~tspsu)

```


```{r}
modelsummary(
  list(
    "Food Low"       = fs_fn,
    "Very Low FS"    = vlfs_fn,
    "HEI Total"      = hei_fn,
    "BMI"            = bmi_fn,
    "Obese"          = ob_fn,
    "Severely Obese" = sob_fn
  ),
  coef_map = c("false_neg" = "False Negative"),
  stars = TRUE,
  title = "Table 8d. Regression Results using False Negative",
  output = "markdown",
  fmt = 3,
  gof_omit = ".*"
)
```

### False Positive Regressions
```{r include=FALSE}
fs_fp <- feols(as.formula(paste0("foodsec_low ~ ", snap_fp, " + ", controls)),
               data = Table4_sample, weights = ~hhwgt, cluster = ~tspsu)

vlfs_fp <- feols(as.formula(paste0("foodsec_verylow ~ ", snap_fp, " + ", controls)),
                 data = Table4_sample, weights = ~hhwgt, cluster = ~tspsu)

hei_fp <- feols(as.formula(paste0("hei_total ~ ", snap_fp, " + ", controls)),
                data = Table4_sample, weights = ~hhwgt, cluster = ~tspsu)

bmi_fp <- feols(as.formula(paste0("BMI ~ ", snap_fp, " + ", controls)),
                data = Table4_sample, weights = ~hhwgt, cluster = ~tspsu)

ob_fp <- feols(as.formula(paste0("Obese ~ ", snap_fp, " + ", controls)),
               data = Table4_sample, weights = ~hhwgt, cluster = ~tspsu)

sob_fp <- feols(as.formula(paste0("Severely_Obese ~ ", snap_fp, " + ", controls)),
                data = Table4_sample, weights = ~hhwgt, cluster = ~tspsu)

```


```{r}
modelsummary(
  list(
    "Food Low"       = fs_fp,
    "Very Low FS"    = vlfs_fp,
    "HEI Total"      = hei_fp,
    "BMI"            = bmi_fp,
    "Obese"          = ob_fp,
    "Severely Obese" = sob_fp
  ),
  coef_map = c("false_pos" = "False Positive"),
  stars = TRUE,
  title = "Table 8e. Regression Results using False Positive",
  output = "markdown",
  fmt = 3,
  gof_omit = ".*"
)
```


### Misreporting Regressions
```{r include=FALSE}
fs_mis <- feols(as.formula(paste0("foodsec_low ~ ", misrep, " + ", controls)),
                data = Table4_sample, weights = ~hhwgt, cluster = ~tspsu)

vlfs_mis <- feols(as.formula(paste0("foodsec_verylow ~ ", misrep, " + ", controls)),
                  data = Table4_sample, weights = ~hhwgt, cluster = ~tspsu)

hei_mis <- feols(as.formula(paste0("hei_total ~ ", misrep, " + ", controls)),
                 data = Table4_sample, weights = ~hhwgt, cluster = ~tspsu)

bmi_mis <- feols(as.formula(paste0("BMI ~ ", misrep, " + ", controls)),
                 data = Table4_sample, weights = ~hhwgt, cluster = ~tspsu)

ob_mis <- feols(as.formula(paste0("Obese ~ ", misrep, " + ", controls)),
                data = Table4_sample, weights = ~hhwgt, cluster = ~tspsu)

sob_mis <- feols(as.formula(paste0("Severely_Obese ~ ", misrep, " + ", controls)),
                 data = Table4_sample, weights = ~hhwgt, cluster = ~tspsu)

```

```{r}
modelsummary(
  list(
    "Food Low"       = fs_mis,
    "Very Low FS"    = vlfs_mis,
    "HEI Total"      = hei_mis,
    "BMI"            = bmi_mis,
    "Obese"          = ob_mis,
    "Severely Obese" = sob_mis
  ),
  coef_map = c("misrep" = "Misrepresentation"),
  stars = TRUE,
  title = "Table 8f. Regression Results using Misrepresentation",
  output = "markdown",
  fmt = 3,
  gof_omit = ".*"
)
```

